Figures main manuscript

### 2020-03-30 code/05_figures-and-correlations.rmd
Updated and made sure bootstrapped values are reproducible in 'heterogeneity and effect sizes' section

#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript (not printed if .rmd is knit)

#1. Standardized mean differences----
SMDs <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
  filter(effect_type == "Standardized Mean Difference")

cor.test(SMDs$tau, SMDs$eff_size) #pearson tau2
cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
cor.test(SMDs$H2, SMDs$eff_size) #pearson H2

cor.test(SMDs$tau, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman

##Excluding anchoring effects
dropped_anchoring <- SMDs %>%
  filter(!grepl("Anchoring", effect))

cor.test(dropped_anchoring$tau, dropped_anchoring$eff_size) #pearson
cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson
cor.test(dropped_anchoring$H2, dropped_anchoring$eff_size) #pearson

#1.05 When ES not sig. diff from zero----
##When effect size not sig diff from 0 (alpha = .05), what is average heterogeneity?
nrow(SMDs[SMDs$eff_size_p > 0.05,]) #20/40 SMDs have ES not sig. diff from zero
sum(SMDs$tau[SMDs$eff_size_p > 0.05] == 0) #13/20 of these have taus == 0

@@

#logs
logOR <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
  filter(effect_type == "Log Odds Ratio")

@@

#bootstrap confidence intervals
#code contribution by Amir Abdol

#1.1 I2 confidence intervals----

#bootfit <- boot(data=SMDs, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
#I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#Excluding anchoring effects
set.seed(234)
bootfit <- boot(data=dropped_anchoring, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #statistic function is sourced

I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#1.2 Tau confidence intervals----

# bootfit <- boot(data=tau_per_type, statistic=pear_tau, R=1000, formula= ~ eff_size + tau2) #see Fig 3
# tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

#Excluding anchoring effects
cor.test(dropped_anchoring$tau2, dropped_anchoring$eff_size)

set.seed(423)
bootfit <- boot(data=dropped_anchoring, statistic=pear_tau, R=1000, formula= ~ eff_size + tau)
tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#1.3 H2 confidence intervals----
set.seed(342)
bootfit <- boot(data=tau_per_type, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

#1.4 spearman bootstrap CIs----
#First for I2
spear_I2 <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

set.seed(241)
options(warn=-1)
bootfit <- boot(data=tau_per_type, statistic=spear_I2, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))

#Second for tau

set.seed(5233)
options(warn=-1)
bootfit <- boot(data=tau_per_type, statistic=spear_tau, R=1000, formula= ~ eff_size + tau)
options(warn=0)

tau_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))

>>>>

#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript (not printed if .rmd is knit).

#bootstrap confidence intervals code contribution by Amir Abdol.

set.seed(435) #same seed as for plot

#Pearson bootstrap percentile confidence intervals for SMD and logOR
cis <- tau_per_type %>% #same as in Figure 3
  split(.$effect_type) %>% 
  map_dfr(bootfitter, .id = "effect_type") #bootfitter is a sourced function

#1.1. Standardized mean differences Pearsons----
SMDs <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
  filter(effect_type == "Standardized Mean Difference")

#pearson tau2
cor.test(SMDs$tau, SMDs$eff_size) 
#pearson I2
cor.test(SMDs$s_I2, SMDs$eff_size)
#pearson H2
cor.test(SMDs$H2, SMDs$eff_size)

#1.2. log OR Pearson's----
logOR <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
  filter(effect_type == "Log Odds Ratio")

#pearson tau2
cor.test(logOR$tau, logOR$eff_size) 
#pearson I2
cor.test(logOR$s_I2, logOR$eff_size)
#pearson H2
cor.test(logOR$H2, logOR$eff_size)

#1.3 Excluding anchoring effects Pearson's ---- 
dropped_anchoring <- SMDs %>%
  filter(!grepl("Anchoring", effect))

#tau
cor.test(dropped_anchoring$tau, dropped_anchoring$eff_size) 
bootfit <- boot(data=dropped_anchoring, statistic=pear_tau, R=1000, formula= ~ eff_size + tau)
boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#I2
cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson
bootfit <- boot(data=dropped_anchoring, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #statistic function is sourced
boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#H2
cor.test(dropped_anchoring$H2, dropped_anchoring$eff_size) #pearson
bootfit <- boot(data=dropped_anchoring, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
boot.ci(bootfit, type=c("perc", "bca"))

#1.4. Spearman's rank order correlation----

#tau
cor.test(SMDs$tau, SMDs$eff_size, method = "spearman") #spearman
options(warn=-1)
bootfit <- boot(data=SMDs, statistic=spear_tau, R=1000, formula= ~ eff_size + tau)
options(warn=0)

boot.ci(bootfit, type=c("perc", "bca"))

#I2
cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
options(warn=-1)
bootfit <- boot(data=SMDs, statistic=spear_I2, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

boot.ci(bootfit, type=c("perc", "bca"))

#H2

cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman
options(warn=-1)
bootfit <- boot(data=SMDs, statistic=spear_H2, R=1000, formula= ~ eff_size + H2)
options(warn=0)

boot.ci(bootfit, type=c("perc", "bca"))

#2. When ES not sig. diff from zero----

##When effect size not sig diff from 0 (alpha = .05), what is average heterogeneity?
nrow(SMDs[SMDs$eff_size_p > 0.05,]) #20/40 SMDs have ES not sig. diff from zero
sum(SMDs$tau[SMDs$eff_size_p > 0.05] == 0) #13/20 of these have taus == 0

@@

#logs

@@
